### 2016-07-13 Virt_Real.tex
K factor MRSSM contour plot
K factors in thesis

\subsection{Virtual Correction}

@@

f_{P_i / H}(x,\mu_f) = f(x) + \left( -\frac{1}{\epsilon} \right)\left[ \frac{\alpha_s}{2\pi} \frac{\Gamma(1-\epsilon)}{\Gamma(1-2\epsilon)} \left( \frac{4\pi\mu_R^2}{\mu_F^2} \right)^\epsilon\right] \int_1^x\frac{\mathrm{d}z}{z} P_{P_i P_j}(z)f_{P_j / H}(\frac{x}{z}).

@@

\subsubsection{Real Quark Radiation}\label{sec:RealQuarkRad}
As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences. However, there is a further contribution to squark production at next-to-leading order. This involves the radiation of an additional antiquark in the final state. To meet color conservation, the initial state has to be composed of a quark and a gluon, see fig. \ref{fig:quarkradiation}.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
\begin{scope}[shift={(0,0.25)}]
	\draw[fermion] (-1.25,0.75)--(-0.5,0);
	\draw[gluon] (-1.25,-0.75)--(-0.5,0);
	\draw[fermion] (-0.5,0)--(0.5,0); 
	\draw[scalar] (0.5,0)--(1.25,0.75);
	\draw[gluon] (0.5,0)--(1.25,-0.75);
	\draw[fermionnoarrow] (0.5,0)--(1.25,-0.75);
	\draw[scalar] (1.25,-0.75)--(2,0);
	\draw[fermion] (2,-1.5)--(1.25,-0.75);
	\end{scope}
\begin{scope}[shift={(3,0)}]
	\draw[fermion] (0,1)--(1,1);	
	\draw[gluon] (0,-0.5)--(1,-0.5);
	\draw[fermionnoarrow] (1,1)--(1,-0.5);
	\draw[gluon] (1,1)--(1,-0.5);
	\draw[scalar] (1,1)--(2.75,1);
	\draw[fermionnoarrow] (1,-0.5)--(2,-0.5);
	\draw[gluon] (1,-0.5)--(2,-0.5);
	\draw[scalar] (2,-0.5)--(2.75,0.25);
	\draw[fermion] (2.75,-1.25)--(2,-0.5);
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermion] (0,1)--(1,1);
	\draw[gluon] (0,-1)--(1,-1);
	\draw[fermionnoarrow] (1,1)--(1,0);
	\draw[gluon] (1,1)--(1,0);
	\draw[fermion] (1,-1)--(1,0);
	\draw[scalar] (1,1)--(2,1);
	\draw[fermion] (2,-1)--(1,-1);
	\draw[scalar] (1,0)--(2,0);
\end{scope}
\end{tikzpicture}
\caption{A selection of real quark emission diagrams contributing to squark production. The first two diagrams have a gluino propagator which may go on-shell. In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\label{fig:quarkradiation}
\end{center}
\end{figure}
These contributions do not comprise soft divergences, as they are associated with a different initial state and the factorization theorem guarantees the absences of soft divergences in each initial state separately. In other words, real correction, coming from an initial state with quark and gluon, cannot contribute to the cancellation of soft divergences with virtual correction which are associated with two quarks in the initial state.\\
A split-up of space space in a soft and a hard part is therefore not needed. However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of \ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
But there is another complication: The first and second diagram in fig. \ref{fig:quarkradiation} include a gluino which subsequently decays into a squark-antiquark pair. If the squared gluino's four-momentum approaches its mass-shell $p^2 = m^2_{\tilde{g}}$ the amplitude of this diagram hits a singularity. Of course, this can only happen if $m_{\tilde{g}} > m_{\tilde{q}}$.\\
These singularities are treated by introducing a non-zero width $\Gamma_{\tilde{q}}$ for the gluino as a regulator, i.e. modifying the propagator to the Breit-Wigner form
\begin{align}
\frac{1}{p^2 - m_{\tilde{q}}^2} \to \frac{1}{p^2 - m_{\tilde{q}}^2 + i m_{\tilde{q}} \Gamma_{\tilde{q}}}.
\end{align}
Integrating over the regime of phase space, where the gluino approaches its mass-shell, actually gives the tree-level contribution of the process $qG \to \tilde{q}\tilde{g}$ weighted by the branching ratio $\frac{\Gamma_{\tilde{q}\to q \tilde{g}}}{\Gamma_{\tilde{q}}}$. To avoid double counting, one has to cut this very regime of phase space out and subtract it from the total contribution originating from those diagrams. For a detailed prescription on how to deal with this issue, see \cite{Beenakker:1996ch, Gavin:2013kga}.

>>>>

\subsection{Virtual Corrections}

@@

f_{P_i / H}(x,\mu_f) = f(x) + \left( -\frac{1}{\epsilon} \right)\left[ \frac{\alpha_s}{2\pi} \frac{\Gamma(1-\epsilon)}{\Gamma(1-2\epsilon)} \left( \frac{4\pi\mu_R^2}{\mu_F^2} \right)^\epsilon\right] \int_1^x\frac{\mathrm{d}z}{z} P_{P_i P_j}(z)f_{P_j / H}(\frac{x}{z}).\label{eq:renpdf}

@@

\subsubsection{Real Quark Radiation}\label{sec:RealQuarkRad}
As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences. However, there is a further contribution to squark production at next-to-leading order. This involves the radiation of an additional antiquark in the final state. To meet color conservation, the initial state has to be composed of a quark and a gluon, see fig. \ref{fig:quarkradiation}.
\begin{scope}[shift={(0,0.25)}]
	\draw[fermion] (-1.25,0.75)--(-0.5,0);
	\draw[gluon] (-1.25,-0.75)--(-0.5,0);
	\draw[fermion] (-0.5,0)--(0.5,0); 
	\draw[scalar] (0.5,0)--(1.25,0.75);
	\draw[gluon] (0.5,0)--(1.25,-0.75);
	\draw[fermionnoarrow] (0.5,0)--(1.25,-0.75);
	\draw[scalar] (1.25,-0.75)--(2,0);
	\draw[fermion] (2,-1.5)--(1.25,-0.75);
\begin{scope}[shift={(3,0)}]
	\draw[gluon] (0,-0.5)--(1,-0.5);
	\draw[fermionnoarrow] (1,-0.5)--(2,-0.5);
	\draw[gluon] (1,-0.5)--(2,-0.5);
	\draw[scalar] (2,-0.5)--(2.75,0.25);
	\draw[fermion] (2.75,-1.25)--(2,-0.5);
\begin{scope}[shift={(7,0)}]
	\draw[gluon] (0,-1)--(1,-1);
	\draw[fermion] (2,-1)--(1,-1);
\caption{A selection of real quark emission diagrams contributing to squark production. The first two diagrams have a gluino propagator which may go on-shell. In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\label{fig:quarkradiation}
These contributions do not comprise soft divergences, as they are associated with a different initial state and the factorization theorem guarantees the absences of soft divergences in each initial state separately\cite{dissertori2003quantum}. This can be seen by inspecting eq. \eqref{eq:facTheorem} with the leading order parton density function replaced by the renormalized parton density function from eq. \eqref{eq:renpdf}. As the left hand side of eq. \eqref{eq:facTheorem} is free of soft (and collinear) divergences, also the right hand side has to be infrared finite. Furthermore, the renormalized parton density functions are free of soft divergences, so the partonic cross section in eq. \eqref{eq:facTheorem} needs also be be free of soft divergences. In other words, real corrections, coming from an initial state with quark and gluon, cannot contribute to the cancellation of soft divergences with virtual corrections which are associated with two quarks in the initial state.\\
A split-up of space space in a soft and a hard part is therefore not needed. However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of \ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
But there is another complication: The first and second diagram in fig. \ref{fig:quarkradiation} include a gluino which subsequently decays into a squark-antiquark pair. If the squared gluino's four-momentum approaches its mass-shell $p^2 = m^2_{\tilde{g}}$ the amplitude of this diagram hits a singularity. Of course, this can only happen if $m_{\tilde{g}} > m_{\tilde{q}}$.\\
These singularities are treated by introducing a non-zero width $\Gamma_{\tilde{q}}$ for the gluino as a regulator, i.e. modifying the propagator to the Breit-Wigner form
\frac{1}{p^2 - m_{\tilde{q}}^2} \to \frac{1}{p^2 - m_{\tilde{q}}^2 + i m_{\tilde{q}} \Gamma_{\tilde{q}}}.
Integrating over the regime of phase space, where the gluino approaches its mass-shell, actually gives the tree-level contribution of the process $qG \to \tilde{q}\tilde{g}$ weighted by the branching ratio $\frac{\Gamma_{\tilde{q}\to q \tilde{g}}}{\Gamma_{\tilde{q}}}$. To avoid double counting, one has to cut this very regime of phase space out and subtract it from the total contribution originating from those diagrams. For a detailed prescription on how to deal with this issue, see \cite{Beenakker:1996ch, Gavin:2013kga}.
